---
title: "carseats"
author: "sara navarro medina"
date: "10/01/2022"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(arules)
library(sjstats)
library(ggplot2)
library(R.matlab)
library(ISLR)
library(ggsci)
library(hrbrthemes)

df = ISLR::Carseats
head(df)
```

```{r}
# Display Structure of Data Frame.
str(df)
```

```{r}
# Check nulls per variable.
lapply(df,function(x) { length(which(is.na(x)))})
```

Variables do not have null values.
```{r}
# Select just numerical features
nums <- unlist(lapply(df, is.numeric))

for (var in names(df[, nums])) {
  print(var)
  print(summary(df[,c(var)]))
  boxplot(df[,c(var)], main = paste0(var," boxplot"))
}
```

```{r}
# Select just categorical features
cat <- unlist(lapply(df, is.factor))

for (var in names(df[, cat])) {
  print(var)
  print(table(df[,c(var)]))
  print(round(prop.table(table(df[,c(var)])),2))
}
```
There are twice as many stores with car seats on the middle shelf as stores with car seats on the bad or good shelf.

30% of the stores are in rural areas.

36% of stores are not in the US.

```{r}
# New variable with ages by interval
df$Age_cat <- cut(df$Age, breaks = c(25,30,35,40,45,65,80),
      labels = c("25-30","30-35","35-40","40-45","45-65","65-80"),
      include.lowest = TRUE)
# New variable with sales classified as low, medium, high and very high
df$Sales_cat <- cut(df$Sales, breaks = c(0,5.39,7.49,9.32,16.27), labels = c("bajas", "medias","altas","muy altas"),include.lowest = TRUE)

# New variable with the price difference between the stores and their competencies in absolute value
df$diff_price <- abs(df$Price - df$CompPrice)
```

# Analysis of the price variable
### The higher the price, the higher the price of the competition?
```{r}
plot(x = df$Price, y = df$CompPrice, main="Price VS CompPrice", xlab="Price",ylab="Competence Price", col = alpha("black", 0.5), pch = 19)
```

There is a clear correlation between the price of the store and that of its competition.

### The distribution of the price of the car seat according to the sales in the stores are high, medium or low.
```{r}
ggplot(df, aes(x=Sales_cat, y=Price)) + 
    geom_boxplot() + theme_ipsum() +
    labs(title = "Sales level price distribution", x ="Level Sales", y = "Price")
```

The price of the car seat is negatively correlated with sales: the lower the sales, the higher the price.

### Is the price of car seats very different in stores with low sales in rural and urban areas?
```{r}
ggplot(df, aes(x=Sales_cat, y=Price, color=Urban)) + scale_color_brewer(palette = "Paired") +
    geom_boxplot() + theme_ipsum() + labs(title = "Sales level price distribution by area", x ="Level Sales", y = "Price")
```

Car seat price is negatively correlated with sales in urban areas.
However, in rural areas, mid-category sales are somewhat higher than low-category sales.

### At a higher price, is the difference between the price of the car seat and that of the competition lower?
```{r}
ggplot(df, aes(x=Price, y=diff_price)) + 
    geom_point(
        fill="black",
        shape=21,
        alpha=0.5,
        size=3
        ) + theme_ipsum() + labs(title = "Price VS Price difference between shops and competition", x ="Price", y = "Price difference between shops and competition")
```

There is a tendency that the higher the price, the lower the price difference of the car seat with the competition.

### How is the difference between the price of the car seat and the price of the competition distributed?
```{r}
boxplot(df$diff_price, main = "Car seat price difference between shops and competition")
summary(df$diff_price)
```

3/4 parts have a difference between the price of the car seat and the price of the competition of 25 dollars or less.

### Is the price of the competition higher if the price of the car seat in the store is higher?
```{r}
plot(x=df$Price, y=df$CompPrice, main
     = "Price VS CompPrice", ylab = "Competence Price", xlab = "Price", col = alpha("black", 0.5), pch = 19)
```

There is a positive correlation between the price of the car seat in the store and the price of your competition.

### Is the difference between the price of the car seat and that of the competition lower at higher incomes?
```{r}
ggplot(df, aes(x=Price, y=diff_price, size=Income,color=Income)) + 
    geom_point(alpha=0.5) + theme_ipsum() + scale_color_gradient(low = "#FF410DFF", high = "#6EE2FFFF") +
    labs(title = "Price difference with the competition VS Price VS Income", x ="Price", y = "Price difference with the competition")

df$highlow_income <- ifelse(df$Income >= 91, "high_income","nothigh_income")
ggplot(df, aes(x=Price, y=CompPrice, color=highlow_income)) + 
    geom_point(size=3,alpha=0.7) + theme_ipsum() + scale_color_brewer(palette = "Paired") +
    labs(title = "Competition price VS Price VS Income", x ="Price", y = "Competition price")
```

There is no correlation between the different income and price and the difference in price of the car seat with the competition.

# Analysis of the sales variable
### Are dollar sales more the more units are sold?
```{r}
plot(x=df$Price, y=df$Sales, main = "Price VS Sales",  ylab = "Sales", xlab = "Price", col = alpha("black", 0.5), pch = 19)
```

There is a clear relationship between price and sales.

At higher prices there is a tendency to sell fewer car seats.
```{r}
plot(x=df$Price * df$Sales, y=df$Sales, main = "Sales Money VS Sales Quantity",  ylab = "Sales Quantity", xlab = "Sales Money", col = alpha("black", 0.5), pch = 19)
```

The more sales, the more money.

### More sales to more population?
```{r}
plot(x=df$Price * df$Sales, y=df$Population, main = "Sales Money VS Population", ylab = "Population", xlab = "Sales Money", col = alpha("black", 0.5), pch = 19)
```

There is no correlation between the number of inhabitants and sales in money.

### Are there higher sales if there is more income from the community?
```{r}
plot(x = df$Sales_cat, y = df$Income, main="Sales categories VS Income", xlab="Sales categories",ylab="Income")
```

There is a clear relationship between stores with very high sales and community income. The more sales the community income is also higher, and vice versa.

### Sales level by income and area
```{r}
ggplot(df, aes(x=Sales_cat, y=Income, color=Urban)) + scale_color_brewer(palette = "Paired") +
    geom_boxplot() + theme_ipsum() + labs(title = "Income distribution by sales level and area", x ="Level Sales", y = "Income")
```

Low-selling stores in rural areas generally have lower-income customers than stores in urban areas.

Stores with average sales in rural areas generally have customers with lower incomes than stores in urban areas.

High-selling stores in rural areas generally have lower-income customers than stores in urban areas.

High-selling stores in rural areas generally have higher-income customers than stores in urban areas.

### Of the total sales in each area, is there a higher percentage of rural or urban sales depending on whether sales are low, medium, high or very high?
```{r}
summary(df$Sales)

df_sales_urban <- df %>% group_by(Sales_cat, Urban) %>% summarise(n = n(), .groups = 'drop')
df_sales_urban$per_sales_urban <- ifelse(df_sales_urban$Urban == "Yes",round(df_sales_urban$n/sum(df$Urban == "Yes"),2),round(df_sales_urban$n/sum(df$Urban == "No"),2))

ggplot(df_sales_urban, aes(fill=Urban,x=Sales_cat,y=per_sales_urban)) + 
  geom_bar(stat= "identity", position=position_dodge()) +
  theme_ipsum() + scale_fill_brewer(palette = "Paired") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5)) + 
  geom_text(aes(label = per_sales_urban), position = position_dodge(0.9),size=2,vjust = 0) + 
  labs(title = "Percentage of stores with different levels of sales according to the area", x ="Sales category", y = "Percent") +
  theme(plot.title=element_text(size=11))
```

Since there are more stores in urban areas than in rural areas, I do not analyze the quantities, but rather the proportions of each category of sale in each area.

There is almost no difference in proportions in any category of sales between urban and rural areas.

The most notable differences in proportions are that proportionally there are more average sales in the urban area and more high sales in the rural area.

### How are customers in stores with high sales in rural areas?
```{r}
df_highsales_rural <- filter(df, Sales_cat == "altas" & Urban == "No")
lmts <- range(df_highsales_rural$Education,df$Education)

par(mfrow = c(1, 2))
boxplot(df_highsales_rural$Education,ylim=lmts, main="Education with shops with high sales in a rural area",cex.main=0.75)
boxplot(df$Education,ylim=lmts, main="Education for all shops",cex.main=0.75)
```

The distribution of customer education in stores with high sales and in rural areas is higher, in general, than the distribution of education of all customers in all stores.
```{r}
lmts <- range(df_highsales_rural$Age,df$Age)

par(mfrow = c(1, 2))
boxplot(df_highsales_rural$Age,ylim=lmts, main="Age with shops with high sales in a rural area",cex.main=0.75)
boxplot(df$Age,ylim=lmts, main="Age for all shops",cex.main=0.75)
```

There are more young people in stores with high sales and in rural areas.

How many more people?
```{r}
print("Age proportions of customers of stores with high sales in rural areas")
prop.table(table(df_highsales_rural$Age_cat)); 
print("Customer age ratios for all stores")
prop.table(table(df$Age_cat))
```
There are almost 8% more young people in stores with high sales in rural areas than in all stores.

Stores with high sales in rural areas have a higher income community, 8% more youth and more education.

### Do stores with high sales in rural areas put car seats on any particular shelf?
```{r}
print("Car seat shelving ratios of high-selling stores in rural areas")
prop.table(table(df_highsales_rural$ShelveLoc));
print("Car seat shelving ratios for all stores")
prop.table(table(df$ShelveLoc));
```
High-selling stores in rural areas have proportionally half as many car seats on bad shelves as all stores.

### The more sales the car seat is on the better shelf?
```{r}
plot(y = df$Sales, x = df$ShelveLoc, main="Sales VS Shelves", ylab="Sales",xlab="Shelves")
```

The more sales the location of the shelf is the better.

# Analysis of the advertising variable
### Is there more advertising spending in rural or urban areas?
```{r}
df %>% group_by(Urban) %>% summarise(mean_ads = mean(Advertising))
```
```{r}
ggplot(df, aes(x=Urban,y=Advertising)) +
    geom_boxplot() + theme_ipsum() + labs(title = "Investment in advertising distribution by area", x ="Urban", y = "Advertising")

summary(filter(df, Urban== "No")$Income)
summary(filter(df, Urban== "Yes")$Income)
```

The distribution of advertising in urban areas is somewhat higher.

### More advertising more sales?
```{r}
plot(y = df$Sales, x = df$Advertising, main="Sales VS Advertising", ylab="Sales",xlab="Advertising", col = alpha("black", 0.5), pch = 19)
```

There is no correlation between sales and advertising.

### The higher the price, the more investment in advertising?
```{r}
plot(y = df$Advertising, x = df$Sales, main="Sales VS Advertising", ylab="Advertising",xlab="Sales", col = alpha("black", 0.5), pch = 19)
```

There is a slight positive correlation to more advertising more sales.

### Is there an age where there is a stronger correlation between price and advertising?
```{r}
ggplot(df,aes(x=Advertising, y=Sales, size=Age, color=Age_cat)) +
    geom_point(alpha=0.5) + theme_ipsum() + scale_color_brewer(palette = "Paired") +
    labs(title = "Advertising VS Sales VS Age")
ggplot(filter(df,Age>=35),aes(x=Advertising, y=Sales, size=Age, color=Age_cat)) +
    geom_point(alpha=0.5) + theme_ipsum() + scale_color_brewer(palette = "Paired") +
    labs(title = "Advertising VS Sales VS Age (greater than 35 years old)")
```

There is a correlation between advertising and sales for clients over 35 years of age.

### Do those who do not invest in advertising sell on average the same as the rest?
```{r}
summary(filter(df,Advertising==0)$Sales)
summary(filter(df,Advertising>0)$Sales)
```
Those who invest in advertising sell an average of $1,000 more than the rest.

### Do those who invest more in advertising sell car seats arranged in better shelves?
```{r}
ggplot(filter(df,Age>=35),aes(x=Advertising, y=Sales, size=ShelveLoc, color=ShelveLoc)) +
    geom_point(alpha=0.5) + theme_ipsum() + scale_color_brewer(palette = "Paired") +
    labs(title = "Advertising VS Sales VS Shelves")
```

There is a clear correlation between higher sales and better shelf and the rest.

There is no correlation between advertising and shelf location.

# Analysis of the income variable
### Is there more community income in rural or urban areas?
```{r}
ggplot(df, aes(x=Urban,y=Income)) + geom_boxplot() +
    theme_ipsum() + labs(title = "Income distribution by area")
```

The distribution of community income is similar in urban and rural areas.

### Income distribution by age and area
```{r}
ggplot(df, aes(x=Urban, y=Income, color=Age_cat)) + geom_boxplot() +
    theme_ipsum() + scale_color_brewer(palette = "Paired") +
    labs(title = "Income distribution by area and age")
```

For clients between 25-30, 30-35 and 40-45 years old, income distribution is more compact in rural areas.

For clients between 35-40 years of age, income distribution is higher in rural areas.

For clients between 45-65 years of age, income distribution is lower in rural areas.

For clients between 65-80 years of age, income distribution is less compact in rural areas.

```{r}
ggplot(df %>% group_by(Age_cat, Urban) %>% summarise(mean_income = mean(Income),.groups='drop'), aes(fill=Urban,x=Age_cat,y=mean_income)) + geom_bar(stat= "identity", position=position_dodge()) + scale_fill_brewer(palette = "Paired") + theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5)) + geom_text(aes(label = round(mean_income,2)), position = position_dodge(0.9),size=2,vjust = 0) + ggtitle("Average income by age range and area") + ylab("Mean Income") + labs(fill = "Urban") + xlab("Age intervals") + theme_ipsum()
```

The intervals with the greatest difference are 35-40 and 45-65 years.

Customers aged 35-40 in rural areas have a higher average income than those in urban areas.

Customers aged 45-65 in urban areas have a higher average income than those in rural areas.

### Do stores with a community with more income have more investment in advertising?
```{r}
plot(x=df$Income, y=df$Advertising, main = "Income VS Advertising", ylab = "Advertising", xlab = "Income", col = alpha("black", 0.5), pch = 19)
```

There is no correlation between community income and advertising.

### Is the price of car seats more expensive in stores with a community with more income?
```{r}
plot(x=df$Income, y=df$Price, main = "Income VS Price", ylab = "Price", xlab = "Income", col = alpha("black", 0.5), pch = 19)
```

There is no correlation between the price of car seats and the income of the customer community.

### Are there older customers in the community stores with more income?
```{r}
plot(x=df$Income, y=df$Age, main = "Income VS Age", ylab = "Age", xlab = "Income", col = alpha("black", 0.5), pch = 19)
```

There is no correlation between the income of the client community and the ages of the clients.

### Are there more educated customers in stores with a higher income community?
```{r}
plot(x=df$Income, y=df$Education, main = "Income VS Education", ylab = "Education", xlab = "Income", col = alpha("black", 0.5), pch = 19)
```

There is no correlation between customer community income and customer education.

### Are there stores with more sales in the community stores with more income?
```{r}
plot(x=df$Income, y=df$Sales, main = "Income VS Sales", ylab = "Sales", xlab = "Income", col = alpha("black", 0.5), pch = 19)
```

There is no correlation between customer community income and sales.

### Is the arrangement of car seats on the shelves better in the community stores with more income?
```{r}
plot(x=df$Income, y=df$ShelveLoc, main = "Income VS Shelves", ylab = "Shelves", xlab = "Income", col = alpha("black", 0.5), pch = 19)
```

There is no correlation between the income of the customer community and the shelves on which car seats are available.

# Analysis of the customer age variable
### Older, more educated?
```{r}
df %>% group_by(Age_cat) %>% summarise(median_edu = median(Education),.groups = 'drop')
```
```{r}
print("25-30")
quantile(filter(df, Age_cat == "25-30")$Education);
print("30-35")
quantile(filter(df, Age_cat == "30-35")$Education);
print("35-40")
quantile(filter(df, Age_cat == "35-40")$Education);
print("40-45")
quantile(filter(df, Age_cat == "40-45")$Education);
print("45-65")
quantile(filter(df, Age_cat == "45-65")$Education);
print("65-80")
quantile(filter(df, Age_cat == "65-80")$Education)
```
Clients aged 40-65 have less education than other clients.

I analyze if this assessment has to do with being in a rural area or not.

### Are there more stores with customers aged 40-65 in rural or urban areas?
```{r}
prop.table(table(df$Urban))
prop.table(table(filter(df, Age >= 40 & Age <= 65)$Urban))
```
Stores with customers aged 40-65 have the same percentage in rural and urban areas as the total number of stores.

### Is there a difference in the age of customers who buy in rural or urban areas?
```{r}
df_age_urban <- df %>% group_by(Age_cat,Urban) %>% summarise(n = n(),.groups='drop')
df_age_urban$per_age_urban <- ifelse(df_age_urban$Urban == "Yes", round(df_age_urban$n/sum(df$Urban == "Yes"),2),round(df_age_urban$n/sum(df$Urban == "No"),2))
ggplot(df_age_urban, aes(fill=Urban,x=Age_cat,y=per_age_urban)) + geom_bar(stat= "identity", position=position_dodge()) + 
  scale_fill_brewer(palette = "Paired") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5)) + 
  geom_text(aes(label = per_age_urban), position = position_dodge(0.9),size=2,vjust = 0) + 
  ggtitle("Percentage of stores with customers of different ages according to the area") + xlab("age") + ylab("percent") + labs(fill = "urban") +
  theme_ipsum() + theme(plot.title=element_text(size=11))

```

There is not much difference between the ages of clients in urban and rural areas.

Do the youngest clients live more in the city than the rest?

Given that 70% of clients live in the city and 30% of clients live in the countryside, it is logical that there are more young clients living in the city. However, I analyze among all those who live in the city what percentage is young and among all those who live in the countryside what percentage is not young.

Of those who live in the city, 10% are young.

Of those who live in the countryside, 14% are young.

There is almost the same percentage of young people who live in the city and in the countryside if we count total rural clients on the one hand and total urban clients on the other hand.
